Compositional Certified Resource Bounds

### 2015-04-13 paper/main.tex
read through 'Cost Aware Clight'. minor changes

We present the rules for a subset of Clight.
Clight is the first intermediate
language of the CompCert compiler~\cite{CompcertCACM}, it
is a cleaner C with a unified looping construct and
side-effect free expressions.  We reuse most of CompCert's
syntax but instrument the semantics with a resource metric
$M$ that accounts for the cost (an arbitrary rational number)
of each step in the operational semantics.  For example, $M_e(\code{exp})$ is the cost of
evaluating the expression \code{exp}; the rationals $M_f$
and $M_r$ account respectively for the cost of a call to the
function $f$ and the cost of returning from it.
More details are provided in \pref{sec:soundness}.

>>>>

We present the rules for a subset of Clight.
Clight is the first intermediate
language of the CompCert compiler~\cite{CompcertCACM}. It
is a subset of C with a unified looping construct and
side-effect free expressions.  We reuse most of CompCert's
syntax but instrument the semantics with a resource metric
$M$ that accounts for the cost (an arbitrary rational number)
of each step in the operational semantics.  For example, $M_e(\code{exp})$ is the cost of
evaluating the expression \code{exp}. The rationals $M_f$
and $M_r$ account respectively for the cost of a call to the
function $f$ and the cost of returning from it.
More details are provided in \pref{sec:soundness}.
